manuscript_figures

### 2024-06-03 scripts/manuscript_figures.Rmd
makeing maps

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(car)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)

@@

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tigris)
library(car)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(ggmap)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)
library(ggspatial)
if ("ggsn" %in% rownames(installed.packages()) == 'FALSE') BiocManager::install("ggsn")
library(ggsn)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)
```

@@

# Figure 1: organize data and make study site map of a) larger RI and NarrBay with Ft Weatherill and Kings Beach areas in boxes; b) zoom in of the Ft Weatherill box with specific transects as dots; c) zoom in of the Kings Beach box with specific transects as dots.
```{r}
# Create a dataframe with site coordinates
sites <- data.frame(
  Site = c("Fort Weatherill", "King's Beach"),
  Latitude = c(41.477, 41.452),  # Adjusted approximate values for the sites
  Longitude = c(-71.364, -71.326) # Adjusted approximate values for the sites
)

# Convert sites dataframe to an sf object with CRS 4326
sites_sf <- st_as_sf(sites, coords = c("Longitude", "Latitude"), crs = 4326)

# Get Rhode Island state boundaries and set CRS to 4326
ri_state <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>%
  filter(ID == "rhode island")

# Define your rectangle sizes (adjust as needed)
rect_size1 <- 0.01 # Smaller rectangle
rect_size2 <- 0.02 # Larger rectangle

# Function to create rectangles around each site
create_rectangle <- function(site, rect_size) {
  lon <- st_coordinates(site)[1]
  lat <- st_coordinates(site)[2]
  st_as_sf(st_sfc(st_polygon(list(rbind(
    c(lon - rect_size, lat - rect_size), 
    c(lon - rect_size, lat + rect_size), 
    c(lon + rect_size, lat + rect_size), 
    c(lon + rect_size, lat - rect_size), 
    c(lon - rect_size, lat - rect_size)
  )))), crs = st_crs(site))
}

# Apply the create_rectangle function to each site for both rectangle sizes
site_rectangles <- lapply(st_geometry(sites_sf), function(site) {
  rectangle1 <- create_rectangle(site, rect_size1)
  rectangle2 <- create_rectangle(site, rect_size2)
  list(rectangle1, rectangle2)
})

# Combine all rectangles into one sf object
site_rectangles <- do.call(rbind, unlist(site_rectangles, recursive = FALSE))

# Set CRS for combined rectangles
st_crs(site_rectangles) <- st_crs(sites_sf)

# Plot
panelA <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_sf(data = site_rectangles, color = "red2", fill = NA, size = 1) + # Add rectangles around sites
  geom_sf(data = sites_sf, color = "blue", size = 3) + # Add site points for reference
  coord_sf(xlim = c(-72, -71.0), ylim = c(41.1, 42.1), expand = FALSE) + # Zoom level
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(1.1, "in"), pad_y = unit(0.4, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme_classic() # Remove axes and background

panelA
```
